A PVSS scheme ideally has the following properties~\cite{pvss_pairings_heidervand}:
% Uniqueness?
\begin{definition}[Correctness]
    For any committe with public keys $pk$, secret $s$, honest dealer $D$, and $(\hat{s}, \pi_D)$ that $D$ produces, $\textsf{verifyDist}(\hat{s}, pk, \pi_D) = 1$, and for any honest subset of $t$ participants, $\textsf{reconstruct}(s_{i_1}, s_{i_2}, \dots, s_{i_t}) = s$.
\end{definition}
\begin{definition}[Verifiability]
    For any committe with public keys $pk$, proof $\pi_D$, and encrypted secret shares $\hat{s}$, if $\textsf{verifyDist}(\hat{s}, pk, \pi_D) = 1$, then $\hat{s}$ is a valid sharing of some secret for the committee with overwhelming probability.
    Furthermore, for every $1 \leq i \leq |pk|$, if $\textsf{verifyShare}(i, \hat{s}_i, \hat{s}_i', \pi_i)$ passes, then $\hat{s}_i' = s_i$ with overwhelming probability.
\end{definition}
\begin{definition}[Indistinguishability of secrets (IND2)]
    Consider the following game played between the a challenger $\mathcal{C}$ and a PPT adversary $\mathcal{A}$.
    Initially, all participants $p_i$ are under the control of $\mathcal{C}$, however $\mathcal{A}$ can corrupt up any subset of up to $t-1$ participants from line 3 onwards:
    \begin{algorithm}[h]
    \caption{IND2 game in the view of $\mathcal{C}$}
        % Keep state? 
        % Double check corruption
        \begin{algorithmic}[1]
            \CommentLine{$\mathcal{C}$ generates public-private key pairs for each participant}
            \State $(pk_i, sk_i) \gets \textsf{Gen}{1^{\lambda}}$ for each $i \in 1, \dots, n$
            \State $\mathcal{A} \gets (pk_1, \dots, pk_n)$
            \CommentLine{$\mathcal{A}$ begins corrupting participants and sends public keys of corrupted participants to $\mathcal{C}$}
            \State $(pk_{i_1}, \dots, pk_{i_k}) \gets \mathcal{A}$
            \State $x_0, x_1 \getsrandomly \mathcal{A}$
            \State $b \getsrandomly \{0, 1\}$
            \State $\mathcal{A} \gets \textsf{PVSS.genDist}(x_b, (pk_1, \dots, pk_n))$
            \State $b' \gets \mathcal{A}$
            \State \Return $b = b'$
        \end{algorithmic}
    \end{algorithm}
    The adversary's advantage is defined as $|Pr[b = b'] - \frac{1}{2}|$.
    The PVSS scheme is IND2-secret if the advantage is negligible.
\end{definition}

More formally, zkSNARKs have the following properties~\cite{snark_defn,groth_snark}:

\begin{definition}[Completeness]
    $(G, P, V)$ is complete if, for any $C$, $(x_C, w_C) \in \mathcal{R}_C$, and sufficiently large security parameter $\lambda$,
    $$
        Pr \bigl[V(\sigma, x_C, \pi) = 1 \mid (\sigma, \tau) \gets G(1^{\lambda}); \pi \gets P(\sigma, x_C, w_C) \bigr] = 1
    $$
\end{definition}

\begin{definition}[Knowledge Soundness]
    $(G, P, V)$ is knowledge sound if for any prover $P^{\star}$, circuit $C$, $(x_C, w_C) \in \mathcal{R}_C$, PPT adversary $\mathcal{A}$, sufficiently large security parameter $\lambda$, and auxiliary input $z \in \{0, 1\}^{poly(\lambda)}$, there exists a polynomial-size extractor $E$ such that

    \begin{equation*}
        \begin{multlined}
            Pr\bigl[V(\tau, x_C, \pi) = 1 \land (x_C, w_C) \notin \mathcal{R}_C \mid \\
                (\sigma, \tau) \gets G(1^{\lambda});
                (x_C, \pi) \gets P^{\star}(z, \sigma);
                w_C \gets E(z, \sigma)
            \bigr] \leq \textsf{negl}(\lambda)
        \end{multlined}
    \end{equation*}
\end{definition}

\begin{definition}[Zero Knowledge]
    $(G, P, V)$ is knowledge sound if for any $C$, $(x_C, w_C) \in \mathcal{R}_C$, PPT adversary $\mathcal{A}$, sufficiently large security parameter $\lambda$, and auxiliary input $z \in \{0, 1\}^{poly(\lambda)}$, there exists an interactive polynomial-size simulator $S$ such that

    \begin{equation*}
        \begin{multlined}
            Pr\bigl[A(\sigma, \tau, z, \pi) = 1 \mid (\sigma, \tau) \gets G(1^{\lambda}); \pi \gets P(\sigma, x_C, w_C) \bigr] = \\
            Pr\bigl[A(\sigma, \tau, z, \pi) = 1 \mid (\sigma, \tau) \gets G(1^{\lambda}); \pi \gets S(\tau, x_C) \bigr]
        \end{multlined}
    \end{equation*}
\end{definition}

% \begin{definition}[Succinctness]
%     A zkSNARK $(G, P, V)$ is succinct if:
%     \begin{itemize}
%         \item $G, P$ have a runtime of $O(\lambda + |C|)$
%         \item $V$ has a runtime of $O(\lambda + |x_C| + \log |C|)$
%         \item An honestly generated proof $\pi$ has size $O(\lambda + \log |C|)$
%     \end{itemize}
% \end{definition}

\subsection{Ledgers}
A ledger $\mathbb{L}$ is a sequence of transactions $\textsf{tx}_1, \textsf{tx}_2, \dots$ maintained by full nodes operating within a consensus protocol.
The consensus protocol operates in rounds under the synchronous model, and any full node or client may have a different view of $\mathbb{L}$ at any round. 
Denote some party $p$'s view of the ledger at round $r$ as $\mathbb{L}_r^p$.
Any party can create a transaction and request for it to be included in the ledger by full nodes, effectively writing to the ledger.
In a secure consensus protocol, all honestly adopted ledgers are prefixes of one another, and once an honest party writes to the ledger, it is eventually included in an honestly adopted ledger.
More formally, the ledger satisfies the following properties~\cite{popos}:

\begin{definition}[Safety]
    For any honest parties $P_1$, $P_2$ and rounds $r_1 \leq r_2$, $\mathbb{L}_{r_1}^{p_1} \leq \mathbb{L}_{r_2}^{p_2}$.
\end{definition}
\begin{definition}[Liveness]
    For any honest party that submits a transaction at consecutive rounds $r_1, r_2, \dots, r_u$, it is included in $\mathbb{L}_{r_u}^P$ for any honest party $P$.
\end{definition}

Each transaction can be viewed as an update to the ledger's state.
The ledger starts with the genesis state $\textsf{st}_0$.
New states can be computed from the previous state $\textsf{st}$ and the transaction $\textsf{tx}$ by applying a transition function $\delta$.
After genesis, the ledger state would be $\delta(\textsf{st}_0, \textsf{tx}_1)$ after the first transaction, $\delta(\delta(\textsf{st}_0, \textsf{tx}_1), \textsf{tx}_2)$ after the second transaction, and so on.
A ledger is \emph{smart-contract enabled} if $\delta$ is a Turing Machine. % TODO: check?
For our purposes, we consider a smart-contract enabled ledger where all state and transactions are public.

\section{Model and Definition}

Our model consists of an environment $\mathcal{Z}$ containing an adversary $\mathcal{A}$.
All communications within $\mathcal{Z}$ are performed via a synchronous broadcast channel with network delay $\Delta$.
All messages broadcasted by any party reach every other party within the network delay, and $\mathcal{A}$ can delay and tamper with messages up to the network delay.
We assume a Random Oracle Model with $H$ as the Random Oracle function.
Within $\mathcal{Z}$, there is a smart-contract enabled ledger $\mathbb{L}$ that satisfies the Safety and Liveness properties.
Any party may read from the $\mathbb{L}$ or write to $\mathbb{L}$ by submitting a transaction.

At initialization, $\mathcal{Z}$ starts $\mathbb{L}$, at which point all parties can read and write to $\mathbb{L}$.
The environment receives a threshold $t$ from outside.
A committee of size $n$ with private-public key pairs $(sk_i, pk_i)$ is spawned, $t$ of which are honest.
The Cassiopeia smart contract is deployed with the corresponding committee's public keys, $t$, and $\tau$.
Then, the dealer and the extractor are spawned.
The environment generates the common reference string and verification state $\sigma, \tau$ for $C$ (Algorithm~\ref{alg:snark_circuit}) and broadcasts them to all parties.

The environment receives a message $m$ from outside and sends $m$ privately to the dealer.
The dealer then submits a transaction to ledger in the form of $\textsf{Cassiopeia.shareSecret}(c, \pi, x, y)$ where the arguments are generated by the dealer. % Does the transaction always have to be submitted?
TODO: what next?

% \section{Extractable Social Witness Encryption}
% Define game and security properties (correctness, social extractable security)

% Intuitively, the purpose of the commitment $y$ is to ensure non-malleability.
% Without the zkSNARK proof and $y$, the adversary can submit $c$ along with another instance $X'$ of possibly another NP language $\mathcal{L}'$ that they know the witness to and decrypt the honest dealer's secret.
% Since $y$ is the output of a random oracle function, changing $X$ or any other part of the input will scramble the result entirely, so without knowledge of $s$, the adversary cannot produce a commitment $y' = H(s' \concat c' \concat X')$ and a proof of knowledge of the corresponding $s'$ for some ciphertext $c'$ and NP language instance $X'$ such that $s$ can be deduced from $s'$ in polynomial time.